How to Analyze Build Logs --- A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-23 tse-paper/content.tex
easy fixes and prio

% \section{Introduction}
% Todo: Introduction structure
% 0) we introduce & define the problem 1) we survey which techniques
% exist 2) we implement (for a lack of readily available implementations)
% and compare the most promising ones 3) we draw conclusions for when to
% use which technique

% TODO: Include term predictive CI, link to FB paper and
%https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730

@@

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on manually supplied example pairs of build logs and chunks,
  PBE automatically
  synthesizes
  a regular expression extracting the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  % TODO what is the vector space model?
  Using the Vector Space Model, CTS selects lines of a log which are
  most similar to the lines present in manually supplied example chunks.
  \item \textbf{Keyword Search (KWS)}
  % TODO what is an ad-hoc method?
  Ad-hoc method for finding fitting passages by searching the whole
  text of a build log for
  the occurrence of specific trigger words.
\end{itemize}

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the processing of system logs produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

In principle, one can apply the techniques developed for system log
analysis
to parts of the build logs that have this same structure.
% TODO this explanation is not understandable.
It needs to better embedded in the surrounding text
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
However, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this structure and thus require different
bespoke approaches.
% In this article, we focus on extracting a single specified information
% from the build log as a whole with chunk retrieval techniques.
% Chunk
% retrieval techniques are used as a part of log parsing to retrieve the
% values of variable parts in a log message, e.g.\ by using regular
% expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

An initial Google Scholar search for variations of ``build log''
returned more than 2.2 million results (2020-03-15), many of which stem
from unrelated fields such as construction and wood working.
We refined our search criteria to exclude such obvious
non-related fields and also to exclude works on systems
or event logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results
(2020-03-15).
Our replication package documents the full search
queries~\cite{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed.
We included works at large that seemed to bear a resemblence to software
engineering and building software.
We excluded wroks written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here
With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to our literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

@@

% TODO (resolved): RQs mentioned before explicitly stated
Specifically, we were interested in
\begin{itemize}
  \item what information is retrieved from the logs and
  what the retrieved information is used for (\textbf{RQ1.1})
  \item which techniques are used to process the build logs,
  in how much detail they are described, and whether they are published
  as tools (\textbf{RQ1.2})
  \item what kind of build logs are used and the origin of these
  logs.
(\textbf{RQ1.3})
\end{itemize}

@@

Since we had been careful to include rather than exclude borderline
works, this deeper evaluation excluded another 15 articles from the 87
works left after the second filter phase.
Multiple articles were extensions of others.
Of these, we only considered the earliest article which reported on
the processing of build logs.
This excluded another 11 articles.
In sum, we extracted data from 61 articles.

@@

% TODO: add more concrete example, such as use of retrieved x: developer
feedback, build data set
Once we had classified all works, we went into the second phase
(``execution phase'') in which we  grouped tags
together and found synonyms.

@@

% TODO (resolved): RQs just appeared unconnected out of the blue

% TODO: vertical alignment of rows with text to middle so they are aligned with pictograms on the right?
\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}
\toprule
Name			     & Sources	& Frequency	  \\
\midrule
Parser	&
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\
Regular expression
&\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\
Manual inspection  &
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\
Machine Learning  &
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\
\makecell[cl]{Natural Language Processing}	&
\cite{hassan2017change,lou2019history,schulz2017active} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Information Retrieval  &
\cite{hassan2017change,lindqvist2019detection,ren2018automated} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Analysis  &
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Keyword Search	&
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\
Scan  & \cite{clemencic2014new,hibbard2001visualization} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\
Other  &
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
&
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\
None identified  &
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
&
\\
\bottomrule
\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}

@@

% TODO repeat the question in the subsection title?
\subsubsection{Retrieved Information (RQ 1.1)}
% TODO General ref to Figure 4 missing: We answer this question along
% data in Figure 4, and ...
% ?

@@

The majority of articles (46\%) used the outcome of their build log
analysis for research purposes, as shown in \Cref{fig:litsur:use}.
% TOOD What does this mean? Give an example: to drive further research,
for example to categorize the types of compile errors encountered at
Google~\cite{}.
Further uses were giving feedback to developers (10\%) or automatic
on-ward processing of the retrieved information (8\%)
% TODO for example to ...
.

% TODO repeat the question in the subsection title?
\subsubsection{Retrieval Technique (RQ 1.2)}
\Cref{tab:litsur:techniques} presents the techniques that the articles
% TODO: lets use analyzing build logs canonically? Please search text
to eliminate occurrences of processing?
described for processing build logs.
% TODO This is weird.
Last number we have from above is 51.
43 of the 61 articles we inspected mentioned how they are analyzing build
logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs.''
% TODO include citation?
% TOOD maybe make the point here that it is questionable whether this
includes a comprehensive tokenizer, lexer etc.
based solution and that parsing in many cases really meant regexp.
If we could figure that out, then we would assign it to regexp instead.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating} (based on regular expressions),
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
% TODO: based on which technique?,
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
% TODO: based on which technique?
.

\subsubsection{Build Logs}
% TODO using passive where it is unneccessary
The distribution of supported build tools is shown in
\Cref{fig:litsur:log_producer}.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% analyzed logs produced by
Gradle~\cite{gradle2020website}
and 10\% analyzed logs produced by Ant~\cite{ant2020website}.

% TODO remove first part of this paragraph?
Sometimes this limitation to a specific build tool is motivated by
aspects separate from the build log analysis.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.
A larger amount of the articles within our survey, however, limit
themselves to few build tools because their log format varies and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.

@@

% TODO death by passive
The main platform that build logs were collected from is Travis
CI~\cite{travisci2019webpage},
which was used in 38\% cases.
18\% of the articles processed logs from TravisTorrent and 8\% included
build logs from industrial projects.

% TODO perhaps remove this paragraph?
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported processing from two up to 122 million logs.

@@

% TODO: draw a conclusion together with figure 5: if reuse were higher,
lots of effort could be saved?
% discussion about popularity of replication packages adds nothing to
this paper.
We observed very little reuse of build log analysis tools.
This can stem from the fact that publishing replication packages and
research prototypes became popular only in recent years or from the
high specialization of the developed tools in regards to supported
build environments and targeted information.

Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
\Cref{fig:litsur:log_producer} shows that many studies and tools target
only a few distinct build environments (roughly, area A).
% TODO: passive ...
The majority of build environments was however only targeted by one
article each (B).
From this, we follow: (a) there is a nichè for custom parsers or even
specialized plugins integrated into the build process to make post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
wrote, still have the disadvantage of not being able to work on historic
builds.
(b) the large tail of seldomly-investigated environments would benefit
from the existance of a more generic
solution.
% We implement build environment agnostic build log analysis
% techniques, which are customized to a specific project by
% the training examples which the user provides.
% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
% data set we chose for our evaluation covers a broad range of build
% environments.
% % Further, the training examples also specify the log chunk targeted
% by the
% % retrieval, which enable our chunk retrieval techniques to retrieve
% % a broad range of information from build logs.

@@

% TODO: the following paragraphs have nothing to do with a discussion
of the literature survey results.
% what we need is some derivation of the three techniques 1) regex 2)
cts 3) kws, best repeated here in the discussion and then from the lit
survey above, section 2.4.2
For this reason, we are focussing on techniques that run automatically
after being configured through examples or keywords.
Examples consist of logs and corresponding chunks.
The examples and keywords are provided by the user and can simply be
exchanged whenever new cases are introduced.

@@

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example; we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
a substring of the log file text, representing the
substring that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
If PROSE cannot synthesize a program, e.g.,\
because the regular expression
necessary would be too complicated to synthesize, PBE returns the
error message ``no program found.''
% TODO Figure 7 should not come before Figure 6. Figure 6 and 7 should be
% introduced first. This is best-practice anyway: Whenever you mention
% a figure/table the standard sentence should always be: Figure X shows Y,
% on the vertical axis Z and on the horizontal axis D.

\Cref{lst:prose-program-simplified} presents a simplified version
of a program learned from the examples in \Cref{lst:chunk-example}.

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% TODO Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique based on the common
% TODO: the ominuous Vector Space Model again ...
Vector Space Model~\cite{schutze2008introduction}.
The aim is to retrieve those lines from a build log which are most
similar to examples given by the user.

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% TODO Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% TODO: I think it is good, but the VSM is still unexplained. We need a
% (at least) 1-sentence introduction to it, at its first reference
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

% TODO Moritz: you said: some more details here?
% I would not know of any details to add.
%It's really all we are doing
% TODO: You are right, nothing more is necessary

@@

* Try:
  \end{lstlisting}
\end{subfigure}
  \caption{Two examples of log chunks explaining why an Android
  build failed.}
  % TODO Moritz: we can relate this to travistorrent maybe, you told me
  % long ago that this was something your analyzer cannot extract
  \label{lst:chunk-example}
\end{figure}

@@

\subsection{Tool Implementation}
For our comparison study, we implemented each of the chunk retrieval
techniques and a unifying interface.
The unified interface is implemented in Ruby and
calls the separate technique implementations over the command line.
We implemented PBE in C\# based on the Microsoft PROSE
library~\cite{prose2019webpage} and CTS, KWS, and RLR using
R and the text2vec library~\cite{text2vec2019webpage}.
% TODO and passive again ...
The source code of the implementation can be found in our replication
package~\cite{brandt2020chunk-replication} together
with ready-to-use Docker images.

>>>>

% \section{Introduction}
% TODO: Include term predictive CI, link to FB paper and
%https://www-sciencedirect-com.tudelft.idm.oclc.org/science/article/pii/S0164121218301730

@@

\begin{itemize}
  \item \textbf{Program Synthesis by Example (referred to as PBE)}
  Based on manually supplied example pairs of build logs and chunks,
  PBE automatically
  synthesizes
  a regular expression extracting the given chunks within the build logs.
  \item \textbf{Common Text Similarity (CTS)}
  CTS selects lines of a log which are
  most similar to the lines present in manually supplied example chunks.
  \item \textbf{Keyword Search (KWS)}
  KWS finds fitting passages by searching the whole
  text of a build log for
  the occurrence of specific trigger words.
\end{itemize}

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A field related to build log analysis is the analysis of system
logs which are produced during runtime of the system.
The first difference here is that build logs are produced during runtime
of the build of the system, not the system itself.
In terms of the contents of the logs, the main difference is that system
logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

In principle, one can apply the techniques developed for system log
analysis
to parts of the build logs that have this same structure.
% TODO this explanation is not understandable.
%It needs to better embedded in the surrounding text
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
However, almost all of the techniques developed to analyze system logs
leverage their inherent event structure.
Build logs generally lack this structure and thus require different
bespoke approaches.
% In this article, we focus on extracting a single specified information
% from the build log as a whole with chunk retrieval techniques.
% Chunk
% retrieval techniques are used as a part of log parsing to retrieve the
% values of variable parts in a log message, e.g.\ by using regular
% expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

An initial Google Scholar search for variations of ``build log''
returned more than 2.2 million results (2020-03-15), many of which stem
from unrelated fields such as construction and wood working.
We refined our search criteria to exclude such obvious
non-related fields and also to exclude works on systems
or event logs (see \Cref{sec:system-log-analysis}).
This left us with 1,552 search results
(2020-03-15).
% Our replication package documents the full search
% queries~\cite{brandt2020chunk-replication}.
To make handling so many search results feasible, we employed a
three-pass filtering strategy:

First, we filtered articles based on (a) their title and (b) the
contextual information Google Scholar displayed.
We included works at large that seemed to bear a resemblance to software
engineering and building software.
We excluded works written in a language unintelligible to the authors
(i.e., not English or German), which disregarded fewer than 1\% of search
hits.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We removed further duplicates based on the title and were
left with 256 (16\%) of the original search results.
% removed duplicates of data extraction pass already here
With these 256 remaining articles, we followed a backward snowball
sampling for related work.
If an article referenced a new work in the context
of build log analysis, we added the new one to our literature set.
This added five articles (eight before
duplicate elimination), leading to a total of 261
works.

@@

Specifically, we were interested in
\begin{itemize}
  \item what information is retrieved from the logs and
  what the retrieved information is used for (\textbf{RQ1.1})
  \item which techniques are used to process the build logs,
  in how much detail they are described, and whether they are published
  as tools (\textbf{RQ1.2})
  \item what kind of build logs are used and the origin of these
  logs.
(\textbf{RQ1.3})
\end{itemize}

@@

Since we had been careful to include rather than exclude borderline
works, this deeper evaluation excluded another 15 articles from the 87
works left after the second filter phase.
Multiple articles were extensions of others.
Of these, we only considered the earliest article which reported on
the analyzing of build logs.
This excluded another 11 articles.
In sum, we extracted data from 61 articles.

@@

% TODO: add more concrete example, such as use of retrieved x: developer
%feedback, build data set
Once we had classified all works, we went into the second phase
(``execution phase'') in which we  grouped tags
together and found synonyms.

@@

\addtolength{\tabcolsep}{-5pt}
\begin{table*}[tbhp]
\tinyish
\centering
\caption{Overview of build log analysis techniques.}
\begin{tabularx}{\textwidth}{@{}lXl@{}}

\toprule
Name			     & Sources	& Frequency	  \\
\midrule

\raisebox{0.8mm}{Parser} &
\raisebox{0.8mm}{
\cite{vassallo2018un-break,zhang2016android,seo2014programmers,hassan2019tackling,hassan2017automatic,chromy2007integration,mesbah2019deepdelta,wen2018blimp,kwon2018prioritizing,adams2007design,rahman2018impact,brandyberry2006continuous,tomassi2019bugswarm,ren2018automated,vassallo2019automated,cavalcanti2019impact,sippola2013qt,felipe2012towards,shi2018evaluating,urli2018design,selberg2012use}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_21.pdf}
\\

\raisebox{0.8mm}{Regular expression} &
\raisebox{0.8mm}{
\cite{beller2017oops,hassan2017change,macho2018automatically,vassallo2017a-tale,lou2019history,hassan2017automatic,rott2019empirische,zampetti2019study,zhao2018comparing,rausch2017empirical,ghaleb2019studying,zampetti2017open,zhang2019large,kavaler2019tool,morris2010experience}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_15.pdf}
\\

\raisebox{0.8mm}{Manual inspection} &
\raisebox{0.8mm}{
\cite{sulir2016quantitative,hassan2017automatic,bouabana2019theory,barinov2017applying,silva2018build,ghaleb2019empirical,marcozzi2019systematic,hukkanen2015adopting,rausch2017empirical,hassan2017mining,zolfagharinia2017not,cassee2019impact}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_12.pdf}
\\

\raisebox{0.8mm}{Machine Learning} &
\raisebox{0.8mm}{
\cite{hassan2017change,lou2019history,lindqvist2019detection,ren2018automated,schulz2017active}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_5.pdf}
\\

\raisebox{0.8mm}{Natural Language Processing}	&
\raisebox{0.8mm}{
\cite{hassan2017change,lou2019history,schulz2017active}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Information Retrieval} &
\raisebox{0.8mm}{
\cite{hassan2017change,lindqvist2019detection,ren2018automated}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Analysis} &
\raisebox{0.8mm}{
\cite{sulir2016quantitative,haghighatkhah2018test,durieux2019critical}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Keyword Search} &
\raisebox{0.8mm}{
\cite{brandyberry2006continuous,zhang2019large,kavaler2019tool}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_3.pdf}
\\

\raisebox{0.8mm}{Scan} &
\raisebox{0.8mm}{
\cite{clemencic2014new,hibbard2001visualization}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_2.pdf}
\\

\raisebox{0.8mm}{Other} &
\raisebox{0.8mm}{
\cite{zhang2016android,hassan2017change,lou2019history,silva2018build,ren2018automated,schulz2017active}
} &
\includegraphics[width=0.55\columnwidth]{img/lit-sur/techniques-no-guidelines-cropped_10.pdf}
\\

\raisebox{0.8mm}{None identified} &
\raisebox{0.8mm}{
\cite{macho2017preventing,felipe2012towards,orellana2017differences,madeyski2017continuous,zhao2017impact,santolucito2018statically,makihara2018multi,mcintosh2012evolution,gallaba2018noise,matthies2016scrumlint}
} &
\\

\specialrule{\heavyrulewidth}{0pt}{2pt}

\end{tabularx}
\label{tab:litsur:techniques}
\end{table*}
\addtolength{\tabcolsep}{5pt}

@@

\subsubsection{Which information is targeted? (RQ 1.1)}
% TODO General ref to Figure 4 missing: We answer this question along
% data in Figure 4, and ...
% ?

@@

The majority of articles (46\%) used the outcome of their build log
analysis for research purposes, as shown in \Cref{fig:litsur:use}.
% TODO What does this mean? Give an example: to drive further research,
FIXME
for example to categorize the types of compile errors encountered at
Google~\cite{seo2014programmers}.
Further uses were giving feedback to developers (10\%) or automatic
on-ward processing of the retrieved information (8\%)
% TODO for example to ...
FIXME
.

\subsubsection{Which techniques are used? (RQ 1.2)}
\Cref{tab:litsur:techniques} presents the techniques that the articles
described for analyzing build logs.
43 of the 61 articles we inspected mentioned how they are analyzing
build logs.
However, only 16 of these described their method in detail.

The most mentioned method (34\%) was using a parser, where we also
included
rather imprecise statements like ``we parse the build logs''
~\cite{rahman2018impact}.
% TODO maybe make the point here that it is questionable whether this
%includes a comprehensive tokenizer, lexer etc.
based solution and that parsing in many cases really meant regexp.
If we could figure that out, then we would assign it to regexp instead.
25\% of the articles described the use of regular expressions and 20\%
inspected the logs manually.
Another 8\% employed machine learning such as natural language
processing or information retrieval techniques.
For example,
Seo et al.~\cite{seo2014programmers} developed a custom
parser to classify error messages, while Vassallo et
al.~\cite{vassallo2017a-tale} analyzed build logs with regular
expressions.
Ghaleb et al.~\cite{ghaleb2019studying} used a compound approach.
They started with manual categorizing build logs and selecting
search strings that identify the target category.
Based on the search strings they created a script that automatically
classifies the remaining logs.

Only 25\% of the articles claimed their implementation is available.
Moreover, we
saw some reuse of the few available build log analysis tools.
Five articles employed the tools used to create
\emph{TravisTorrent}~\cite{beller2017travistorrent,beller2017oops,
orellana2017differences,zhao2018comparing} or
an extended version of them~\cite{rott2019empirische,
shi2018evaluating}
% (based on regular expressions),
two used the
\emph{Maven Log Analyzer}~\cite{macho2018automatically,gallaba2018noise}
% based on which technique?,  (based on regular expressions)
another two the
\emph{MAKAO}~\cite{wen2018blimp,adams2007design,adams2007makao} tool
% based on which technique?  (a parser for the output of make files)
.
% I don't think the based on..
adds something here.

% It's all kinda regex.
Even if we say 'parser' it's often regex in the background

\subsubsection{Which build logs are analyzed? (RQ 1.3)}
\Cref{fig:litsur:log_producer} shows the distribution of supported
build tools.
Of the articles we surveyed, 30\% analyzed build logs produced by
Maven~\cite{maven2019website}, 16\% analyzed logs produced by
Gradle~\cite{gradle2020website}
and 10\% analyzed logs produced by Ant~\cite{ant2020website}.

% TODO remove first part of this paragraph?
Sometimes, aspects separate from the build log analysis motivate
this limitation to a specific build tool.
For example, Shi et al.~\cite{shi2018evaluating} focussed on Maven
build logs because they also chose the PIT tool to calculate coverage
and mutation score.
A larger amount of the articles within our survey, however, limit
themselves to few build tools because their log format varies and
therefore ``parsers must be specialized to each build and test
framework''~\cite{tomassi2019bugswarm}.

@@

In 38\% of cases, the articles collected build logs from Travis
CI~\cite{travisci2019webpage}.
18\% of the articles processed logs from TravisTorrent and 8\% included
build logs from industrial projects.

% TODO perhaps remove this paragraph?
% yes it is very unspecific.
however then we have 0 reference
% to how many logs are analyzed
% a central point in our argumentation for automation
The number of logs analyzed varied greatly and we were not always able to
extract it confidently.
Articles reported analyzing from two up to 122 million logs.

@@

% TODO: draw a conclusion together with figure 5: if reuse were higher,
%lots of effort could be saved?
% discussion about popularity of replication packages adds nothing to
this paper.
We observed very little reuse of build log analysis tools.
This can stem from the fact that publishing replication packages and
research prototypes became popular only in recent years or from the
high specialization of the developed tools in regards to supported
build environments and targeted information.

Several articles noted the variety in log formats for different build
environments, which requires customizing build log techniques for
every supported build environment.
\Cref{fig:litsur:log_producer} shows that many studies and tools target
only a few distinct build environments (roughly, area A).
% TODO: passive ...
The majority of build environments was however only targeted by one
article each (B).
From this, we follow: (a) there is a nichè for custom parsers or even
specialized plugins integrated into the build process to make post-factum
parsing of logs redundant.
Plugins  similar to, for example, the Maven plugin to report test
executions Bell et al.
wrote, still have the disadvantage of not being able to work on historic
builds.
(b) the large tail of seldomly-investigated environments would benefit
from the existence of a more generic
solution.
% We implement build environment agnostic build log analysis
% techniques, which are customized to a specific project by
% the training examples which the user provides.
% In addition, the \emph{LogChunks}~\cite{brandt2020logchunks}
% data set we chose for our evaluation covers a broad range of build
% environments.
% % Further, the training examples also specify the log chunk targeted
% by the
% % retrieval, which enable our chunk retrieval techniques to retrieve
% % a broad range of information from build logs.

@@

% TODO: the following paragraphs have nothing to do with a discussion
%of the literature survey results.
% what we need is some derivation of the three techniques 1) regex 2)
%cts 3) kws, best repeated here in the discussion and then from the lit
%survey above, section 2.4.2
For this reason, we are focussing on techniques that run automatically
after being configured through examples or keywords.
Examples consist of logs and corresponding chunks.
The examples and keywords are provided by the user and can simply be
exchanged whenever new cases are introduced.

@@

\subsubsection{Configuration}
In- and output example pairs are the main driver of Programming by
Example; we refer to them in short as \emph{examples}.
The \emph{input} is the text of the build log file.
The \emph{output} is
a substring of the log file text, representing the
substring that should be retrieved by the synthesized program when
given the corresponding input file.
One or multiple examples, the
training set, \emph{configure} a specific chunk retrieval with PBE:
they define the substring of a build log that should be extracted.
The PROSE program synthesis then tries to construct a program
consistent with all training examples.
If PROSE cannot synthesize a program, e.g.,\
because the regular expression
necessary would be too complicated to synthesize, PBE returns the
error message ``no program found.''

% TODO Moritz: you said: The following is very obvious and could apply
% to any
% % technique.
% % kinda.
% It does give a descriptive error message on no match (and
% % that is not possible in other techniques)
% % otherwise yes, nothing interesting happens in the application of pbe
% % though for consistency we might need this section? or merge
% config/application?
% TODO Why does it return an error message? Shouldn't it also return
% <empty string>? Does it not rather return an error message if no
% program can be synthesized?
% TODO Moritz: a regular expression can match an empty string
% and that is different from not finding a match
% it returns error messages in both cases
\subsubsection{Application}
A run of PBE takes a build log file as input and applies the
synthesized regular expression program.
It then returns the substring
of the build log matched by the program or an error message if the
program found no match.

\subsection{Common Text Similarity (CTS)}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique that
retrieve those lines from a build log which are most
similar to examples given by the user.

\subsubsection{Configuration}
To configure chunk retrieval through text similarity we chose to use
the same concept of examples as for PBE
% Moritz: your question was: More details on this.
% How do you
% 'apply' VSM? On what?
% all the following sentences in this subsubsection describe our way
% of determining text similarity which as far as I understand and
% Annibale said is the VSM.
% word tokens, tf-idf, similarity measure
% I added a "as follows", think that is enough for explanation?
% Moritz: I think it is good, but the VSM is still unexplained.
We need a
% (at least) 1-sentence introduction to it, at its first reference
% TODO Moritz: I removed all other references, this is now the first one.
% I hope I got your comment right and now the first and only reference
% is explained :)
and apply the Vector Space Model~\cite{schutze2008introduction}
as follows:
The lines of the output strings of the training examples define our
search query.
The algorithm splits the search query into single lines and
identifies tokens, in our case words.
Then we build a
document-term-frequency matrix over the lines from the search query
and prune very often or very rarely appearing words.
Finally, the
algorithm applies TF-IDF to the matrix, a best practice for natural
language queries~\cite{lee1997document}.

@@

@@

* Try:
  \end{lstlisting}
\end{subfigure}
  \caption{Two examples of log chunks explaining why an Android
  build failed.}
  \label{lst:chunk-example}
\end{figure}

@@

\subsection{Tool Implementation}
For our comparison study, we implemented each of the chunk retrieval
techniques and a unifying interface.
The unified interface is implemented in Ruby and
calls the separate technique implementations over the command line.
We implemented PBE in C\# based on the Microsoft PROSE
library~\cite{prose2019webpage} and CTS, KWS, and RLR using
R and the text2vec library~\cite{text2vec2019webpage}.
